\mytitle{}

### 2019-12-13 paper/paper.tex
Move key source to paper folder---author final.

% !TeX document-id = {b3181d9a-ffe0-4331-a65c-c7fb8f275531}
% !BIB program = biber
\documentclass[10pt, times, comsoc]{IEEEtran}
\usepackage{nopageno}

@@

\hypersetup{
	colorlinks,
	citecolor=black,
	filecolor=black,
	linkcolor=black,
	urlcolor=black,
	pdftitle={\mytitle{}},
	pdfauthor={Kyle A. Simpson, Simon Rogers, Dimitrios P. Pezaros}
%	pdfauthor={Anonymous Giraffe, Anonymous Badger, Anonymous Ibex}
}
\newcommand*{\email}[1]{\href{mailto:#1}{\nolinkurl{#1}} }

@@

\title{\mytitle{}}
\author{
%	Kyle~A.~Simpson\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant number EP/M508056/1].},
	\protect Kyle~A.~Simpson\protect\orcidicon{0000-0001-8068-9909},
%	Kyle~A.~Simpson,
	Simon~Rogers\protect\orcidicon{0000-0003-3578-4477},
%	Simon~Rogers,
	Dimitrios~P.~Pezaros\protect\orcidicon{0000-0003-0939-378X},~\IEEEmembership{Senior~Member,~IEEE,},\\
%	Dimitrios~P.~Pezaros,~\IEEEmembership{Senior~Member,~IEEE,},\\
	School of Computing Science, University of Glasgow, Glasgow, G12 8RZ, UK\\
%	University of Glasgow, Glasgow, Scotland,\\
	\email{k.simpson.1@research.gla.ac.uk}
%Anonymous Giraffe,
%Anonymous Badger,
%Anonymous Ibex\\
%Unnamed Department, Nowhere\\
%\email{giraffe.a@unnamed.com}
}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.65\linewidth]{../plots/ftprep-cap-box}
	\vspace{-0.75cm}
	\caption{
		Learned performance of Instant Control agents when benign traffic is UDP-like, using only a single feature as a basis for decisions.
		Mean IAT, inbound packet sizes, and global state offer the best predictive performance, while most features offer marginal advantage over the unprotected baseline.
		\label{fig:udp-feature-plots}
	}
\vspace{-0.4cm}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.65\linewidth]{../plots/ftprep-tcp-cap-box}
	\vspace{-0.75cm}
	\caption{
		Learned performance of Instant Control agents when benign traffic is TCP-like, using only a single feature as a basis for decisions.
		All of the chosen features can offer a marked improvement over no protection at all.
		Global state and Mean IAT still offer the greatest improvement above baseline, but packet-level statistics are considerably less effective for this class of traffic.
		\label{fig:tcp-cap-feature-plots}
	}
\vspace{-0.7cm}
\end{figure}

\begin{figure}
	\centering
%	\vspace{-0.25cm}
	\includegraphics[width=0.65\linewidth]{../plots/ftprep-tcp-laf-cap-box}
	\vspace{-0.75cm}
	\caption{
		Learned performance of Instant Control agents when benign traffic is TCP-like, combining each feature with the last action taken as a basis for decisions.
		This combination causes a significant improvement in the effectiveness of packet-level and per-window statistics.
		\label{fig:tcp-laf-feature-plots}
	}
\vspace{-0.6cm}
\end{figure}

@@

	\cbstart
	\resizebox{0.8\linewidth}{!}{
		\expandableinput ../tables/tnsm-tree-avg-reward-spiffy.tex
	}
	\cbend
\vspace{-0.25cm}
\end{table}
\begin{table}
	\centering
	\caption{Average reward for combinations of model, host density and traffic class with multiple destinations.\label{tab:av-ecmp-vals}}

	\cbstart
	\resizebox{0.8\linewidth}{!}{
		\expandableinput ../tables/tnsm-ecmp-avg-reward-spiffy.tex
	}
	\cbend
\vspace{-0.5cm}
\end{table}

\subsection{Congestion-unaware traffic}
%\begin{figure}
%	\centering
%	\includegraphics[width=0.9\linewidth]{../plots/udp-2}
%	
%	\caption{
%		Online performance for $n=2$ hosts per egress point when benign traffic is UDP-like.
%		Although Marl++ offers a marked improvement (a peak $\sim$\SI{30}{\percent} more benign traffic arrives unimpeded), SPF significantly underperforms for this relatively simple topology.
%		Non-SPF agents start off reasonably well, slowly learning better policies.
%		\label{fig:udp-2}
%	}
%\end{figure}
%\begin{figure}
%	\centering
%	\includegraphics[width=0.9\linewidth]{../plots/udp-16}
%	
%	\caption{
%		Online performance for $n=16$ hosts per egress point when benign traffic is UDP-like.
%		Marl++ remains marginally ahead of its predecessor, though both have undergone a significant drop in effectiveness.
%		SPF, remarkably, displays performance on par with Marl++ for this more difficult topology.
%		Both of the new models take longer to train, but achieve better peak and average performance than Marl.
%		\label{fig:udp-16}
%	}
%\end{figure}
\begin{figure}
	\centering
	\cbstart
	\includegraphics[width=0.75\linewidth]{../plots/tnsm-udp-box-separate}
	\cbend
	\vspace{-0.3cm}
	\caption{
		Online performance for Opus benign traffic in a single-destination network, multi-agent mode.
%		Marl++ offers a marked improvement (a peak $\sim$\SI{30}{\percent} more benign traffic arrives unimpeded) at small $n$, and remains marginally ahead of its predecessor by $n=16$, though both have undergone a significant drop in effectiveness.
		\emph{Instant} outperforms Marl for $n \in \{4, 8\}$ (with higher variance), but performs similarly to Marl at $n\in \{2, 16\}$.
		\emph{Guarded} underperforms compared to the other agent designs in this problem variant.
%		SPF, remarkably, slightly outperforms Marl++ (with lower variance) for this more difficult topology despite being worse for smaller $n$.
%		Both of the new models take longer to train, but achieve better peak and average performance than Marl.
%		?? REWORK/MAKE ACCURATE
		\label{fig:udp-tree-box}
	}
\vspace{-0.5cm}
\end{figure}

@@

\subsection{Congestion-aware traffic}
%\begin{figure}
%	\centering
%	\includegraphics[width=0.9\linewidth]{../plots/tcp-2}
%	
%	\caption{
%		Online performance for $n=2$ hosts per egress point when benign traffic is TCP-like.
%		Marl++ and Marl achieve very similar performance, starting off similarly well without notable improvement over an episode.
%		SPF's performance is disappointingly close to baseline, indicating that it is as useful as having no defence system.
%		\label{fig:tcp-2}
%	}
%\end{figure}
\begin{figure}
%	\vspace{-0.5cm}
	\centering
	\cbstart
	\includegraphics[width=0.75\linewidth]{../plots/tnsm-tcp-box-single}
	\cbend
	\vspace{-0.3cm}
	\caption{
		Online performance for HTTP benign traffic in a single-destination network, single-agent mode.
		\emph{Instant} and \emph{Guarded} exhibit similar efficacy at $n=2$, protecting less traffic than Marl.
		Only \emph{Guarded}'s performance rapidly increases with $n$, achieving a considerably better median and lower variance than the other models.
		The longer tails of outliers typically indicate the longer training time the new models require---we observe that \emph{Guarded} typically has considerably lower variance once it has converged on a stable policy.
		\label{fig:tcp-tree-box}
	}
\vspace{-0.6cm}
\end{figure}
%\begin{figure}
%	\centering
%	\includegraphics[width=0.95\linewidth]{../plots/tnsm-tcp-box-single}
%	
%	\caption{
%		Online performance for HTTP benign traffic in a single-destination network, single-agent mode.
%		?? DO I need this?
%		\label{fig-tcp-tree-box-single}
%	}
%\end{figure}
\begin{figure}
	\centering
	\vspace{-0.8cm}
	\includegraphics[width=0.75\linewidth]{../plots/tnsm-tcp-16-single}
	\vspace{-0.35cm}
	\caption{
		Online performance of standard and single-agent models in a single-destination network with $n=16$ hosts per egress point, HTTP traffic.
		At this level of host density, \emph{Guarded} reaches higher peak performance sooner and is considerably more consistent throughout the episode.
		\emph{Guarded} benefits greatly from information sharing, converging to protect around \SI{75}{\percent} of TCP traffic within \SI{100}{\second}.
		The \emph{Instant} model converges to Marl's level of performance.
%		With a single agent, Marl++ shows worse performance, while SPF improves significantly and continues to learn well past annealing $\epsilon \rightarrow 0$.
		\label{fig:tcp-tree-16}
	}
%\vspace{-0.5cm}
\end{figure}

@@

\vspace{-0.2cm}
\section*{Acknowledgements}
\vspace{-0.1cm}
Our thanks go to Colin Perkins, Mircea Iordache, Qianru Zhou, Charles Rutherford, Marco Cook and Cristian Urlea for their advice and technical assistance, and to our anonymous reviewers.
%Our thanks go to Anonymous, Anonymous, Anonymous, Anonymous and Anonymous for their advice, comments and technical assistance.
%This work was supported by a nameless funder [grant number 0].
This work was supported in part by the Engineering and Physical Sciences Research Council [grants EP/M508056/1, EP/N033957/1 and EP/P004024/1] and European Cooperation in Science and Technology (COST) Action CA15127: RECODIS---Resilient communication and services.
\vspace{-0.2cm}

\renewcommand*{\bibfont}{\footnotesize}
\printbibliography
%\enlargethispage{-1cm}
\vspace{-1.1cm}
\vskip -6pt plus -1fil
\begin{IEEEbiography}
	[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{authorpics/kyle}}]{Kyle A. Simpson}
	received the MSci degree in computing science from the University of Glasgow in 2017.
	He is currently a PhD student within the Networked Systems Research Laboratory at the School of Computing Science, University of Glasgow.

	Mr.\ Kyle Simpson's research focusses on the use of machine learning and reinforcement learning techniques in cybersecurity and network management, with a core interest in evolving problems and defences.
\end{IEEEbiography}
\vspace{-1.3cm}
\vskip 0pt plus -1fil
\begin{IEEEbiography}
	[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{authorpics/sdr}}]{Simon Rogers}
	received the PhD degree from University of Bristol in 2006. Now he is a Senior Lecturer in the School of Computing Science at the University of Glasgow. Before starting a permanent post in Glasgow he did a couple of Post Doctoral positions (under Mark Girolami).

	Dr.\ Simon Rogers’s research involves the development of machine learning and statistical techniques to help with the analysis of complex datasets, particularly within the field of metabolomics, human-computer interaction and information retrieval.
\end{IEEEbiography}
\vspace{-1.25cm}
\vskip 0pt plus -1fil
\begin{IEEEbiography}
	[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{authorpics/dimitris}}]{Dimitrios P.\ Pezaros}
	(S’01–M’04–SM’14) received the B.Sc. and Ph.D. degrees in computer science from Lancaster University. He is currently a Professor and the Founding Director of the Networked Systems Research Laboratory at the School of Computing Science, University of Glasgow. He is also a visiting Professor at the University of Athens, Department of Informatics and Telecommunications.

	Professor Pezaros has published widely (over 80 peer-reviewed contributions to top-tier international conferences and journals) in the areas of computer communications, network and service management, and resilience of future networked infrastructures, and has received significant funding for his research in the above areas from public funding agencies and the industry. He is a Chartered Engineer, and a senior member of the IEEE and the ACM.

>>>>

% !TeX document-id = {b3181d9a-ffe0-4331-a65c-c7fb8f275531}
% !TeX program = pdflatex
% !BIB program = biber
\documentclass[10pt, times, comsoc]{IEEEtran}
\usepackage{nopageno}

@@

\hypersetup{
	colorlinks,
	citecolor=black,
	filecolor=black,
	linkcolor=black,
	urlcolor=black,
	pdftitle={\mytitle{}},
	pdfauthor={Kyle A. Simpson, Simon Rogers, Dimitrios P. Pezaros}
%	pdfauthor={Anonymous Giraffe, Anonymous Badger, Anonymous Ibex}
}
\newcommand*{\email}[1]{\href{mailto:#1}{\nolinkurl{#1}}}

@@

\title{\mytitle{}}
\author{
%	Kyle~A.~Simpson\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant number EP/M508056/1].},
	\protect Kyle~A.~Simpson\protect\orcidicon{0000-0001-8068-9909},
%	Kyle~A.~Simpson,
	Simon~Rogers\protect\orcidicon{0000-0003-3578-4477},
%	Simon~Rogers,
	Dimitrios~P.~Pezaros\protect\orcidicon{0000-0003-0939-378X},~\IEEEmembership{Senior~Member,~IEEE},\\
%	Dimitrios~P.~Pezaros,~\IEEEmembership{Senior~Member,~IEEE,},\\
	School of Computing Science, University of Glasgow, Glasgow, G12 8RZ, UK\\
%	University of Glasgow, Glasgow, Scotland,\\
	\email{k.simpson.1@research.gla.ac.uk}, \email{Simon.Rogers@glasgow.ac.uk}, \email{Dimitrios.Pezaros@glasgow.ac.uk}
%Anonymous Giraffe,
%Anonymous Badger,
%Anonymous Ibex\\
%Unnamed Department, Nowhere\\
%\email{giraffe.a@unnamed.com}
}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.65\linewidth]{ftprep-cap-box}
	\vspace{-0.75cm}
	\caption{
		Learned performance of Instant Control agents when benign traffic is UDP-like, using only a single feature as a basis for decisions.
		Mean IAT, inbound packet sizes, and global state offer the best predictive performance, while most features offer marginal advantage over the unprotected baseline.
		\label{fig:udp-feature-plots}
	}
\vspace{-0.4cm}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.65\linewidth]{ftprep-tcp-cap-box}
	\vspace{-0.75cm}
	\caption{
		Learned performance of Instant Control agents when benign traffic is TCP-like, using only a single feature as a basis for decisions.
		All of the chosen features can offer a marked improvement over no protection at all.
		Global state and Mean IAT still offer the greatest improvement above baseline, but packet-level statistics are considerably less effective for this class of traffic.
		\label{fig:tcp-cap-feature-plots}
	}
\vspace{-0.7cm}
\end{figure}

\begin{figure}
	\centering
%	\vspace{-0.25cm}
	\includegraphics[width=0.65\linewidth]{ftprep-tcp-laf-cap-box}
	\vspace{-0.75cm}
	\caption{
		Learned performance of Instant Control agents when benign traffic is TCP-like, combining each feature with the last action taken as a basis for decisions.
		This combination causes a significant improvement in the effectiveness of packet-level and per-window statistics.
		\label{fig:tcp-laf-feature-plots}
	}
\vspace{-0.6cm}
\end{figure}

@@

	\cbstart
	\resizebox{0.8\linewidth}{!}{
		\expandableinput tnsm-tree-avg-reward-spiffy.tex
	}
	\cbend
\vspace{-0.25cm}
\end{table}
\begin{table}
	\centering
	\caption{Average reward for combinations of model, host density and traffic class with multiple destinations.\label{tab:av-ecmp-vals}}

	\cbstart
	\resizebox{0.8\linewidth}{!}{
		\expandableinput tnsm-ecmp-avg-reward-spiffy.tex
	}
	\cbend
\vspace{-0.5cm}
\end{table}

\subsection{Congestion-unaware traffic}
%\begin{figure}
%	\centering
%	\includegraphics[width=0.9\linewidth]{../plots/udp-2}
%	
%	\caption{
%		Online performance for $n=2$ hosts per egress point when benign traffic is UDP-like.
%		Although Marl++ offers a marked improvement (a peak $\sim$\SI{30}{\percent} more benign traffic arrives unimpeded), SPF significantly underperforms for this relatively simple topology.
%		Non-SPF agents start off reasonably well, slowly learning better policies.
%		\label{fig:udp-2}
%	}
%\end{figure}
%\begin{figure}
%	\centering
%	\includegraphics[width=0.9\linewidth]{../plots/udp-16}
%	
%	\caption{
%		Online performance for $n=16$ hosts per egress point when benign traffic is UDP-like.
%		Marl++ remains marginally ahead of its predecessor, though both have undergone a significant drop in effectiveness.
%		SPF, remarkably, displays performance on par with Marl++ for this more difficult topology.
%		Both of the new models take longer to train, but achieve better peak and average performance than Marl.
%		\label{fig:udp-16}
%	}
%\end{figure}
\begin{figure}
	\centering
	\cbstart
	\includegraphics[width=0.75\linewidth]{tnsm-udp-box-separate}
	\cbend
	\vspace{-0.3cm}
	\caption{
		Online performance for Opus benign traffic in a single-destination network, multi-agent mode.
%		Marl++ offers a marked improvement (a peak $\sim$\SI{30}{\percent} more benign traffic arrives unimpeded) at small $n$, and remains marginally ahead of its predecessor by $n=16$, though both have undergone a significant drop in effectiveness.
		\emph{Instant} outperforms Marl for $n \in \{4, 8\}$ (with higher variance), but performs similarly to Marl at $n\in \{2, 16\}$.
		\emph{Guarded} underperforms compared to the other agent designs in this problem variant.
%		SPF, remarkably, slightly outperforms Marl++ (with lower variance) for this more difficult topology despite being worse for smaller $n$.
%		Both of the new models take longer to train, but achieve better peak and average performance than Marl.
%		?? REWORK/MAKE ACCURATE
		\label{fig:udp-tree-box}
	}
\vspace{-0.5cm}
\end{figure}

@@

\subsection{Congestion-aware traffic}
%\begin{figure}
%	\centering
%	\includegraphics[width=0.9\linewidth]{../plots/tcp-2}
%	
%	\caption{
%		Online performance for $n=2$ hosts per egress point when benign traffic is TCP-like.
%		Marl++ and Marl achieve very similar performance, starting off similarly well without notable improvement over an episode.
%		SPF's performance is disappointingly close to baseline, indicating that it is as useful as having no defence system.
%		\label{fig:tcp-2}
%	}
%\end{figure}
\begin{figure}
%	\vspace{-0.5cm}
	\centering
	\cbstart
	\includegraphics[width=0.75\linewidth]{tnsm-tcp-box-single}
	\cbend
	\vspace{-0.3cm}
	\caption{
		Online performance for HTTP benign traffic in a single-destination network, single-agent mode.
		\emph{Instant} and \emph{Guarded} exhibit similar efficacy at $n=2$, protecting less traffic than Marl.
		Only \emph{Guarded}'s performance rapidly increases with $n$, achieving a considerably better median and lower variance than the other models.
		The longer tails of outliers typically indicate the longer training time the new models require---we observe that \emph{Guarded} typically has considerably lower variance once it has converged on a stable policy.
		\label{fig:tcp-tree-box}
	}
\vspace{-0.6cm}
\end{figure}
%\begin{figure}
%	\centering
%	\includegraphics[width=0.95\linewidth]{../plots/tnsm-tcp-box-single}
%	
%	\caption{
%		Online performance for HTTP benign traffic in a single-destination network, single-agent mode.
%		?? DO I need this?
%		\label{fig-tcp-tree-box-single}
%	}
%\end{figure}
\begin{figure}
	\centering
	\vspace{-0.8cm}
	\includegraphics[width=0.75\linewidth]{tnsm-tcp-16-single}
	\vspace{-0.35cm}
	\caption{
		Online performance of standard and single-agent models in a single-destination network with $n=16$ hosts per egress point, HTTP traffic.
		At this level of host density, \emph{Guarded} reaches higher peak performance sooner and is considerably more consistent throughout the episode.
		\emph{Guarded} benefits greatly from information sharing, converging to protect around \SI{75}{\percent} of TCP traffic within \SI{100}{\second}.
		The \emph{Instant} model converges to Marl's level of performance.
%		With a single agent, Marl++ shows worse performance, while SPF improves significantly and continues to learn well past annealing $\epsilon \rightarrow 0$.
		\label{fig:tcp-tree-16}
	}
%\vspace{-0.5cm}
\end{figure}

@@

\vspace{-0.2cm}
\section*{Acknowledgements}
\vspace{-0.1cm}
The authors would like to thank Colin Perkins, Mircea Iordache, Qianru Zhou, Charles Rutherford, Marco Cook and Cristian Urlea for their advice and technical assistance, and their anonymous reviewers.
%Our thanks go to Anonymous, Anonymous, Anonymous, Anonymous and Anonymous for their advice, comments and technical assistance.
%This work was supported by a nameless funder [grant number 0].
This work has been supported in part by the UK Engineering and Physical Sciences Research Council [grants EP/N509668/1, EP/N033957/1 and EP/P004024/1] and European Cooperation in Science and Technology (COST) Action CA15127: RECODIS---Resilient communication and services.
\vspace{-0.55cm}

\renewcommand*{\bibfont}{\footnotesize}
\printbibliography
%\enlargethispage{-1cm}
\vspace{-1.1cm}
\vskip -6pt plus -1fil
\begin{IEEEbiography}
	[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{authorpics/kyle}}]{Kyle~A.~Simpson}
	received the MSci degree in computing science from the University of Glasgow in 2017.
	He is currently a PhD student within the Networked Systems Research Laboratory at the School of Computing Science, University of Glasgow.
	His research focusses on the use of machine learning and reinforcement learning techniques in cybersecurity and network management, with a core interest in evolving problems and defences.
\end{IEEEbiography}
\vspace{-1.1cm}
\vskip 0pt plus -1fil
\begin{IEEEbiography}
	[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{authorpics/sdr}}]{Simon~Rogers}
	is a senior lecturer in the School of Computing Science, University of Glasgow. He received his PhD from the department of Engineering mathematics at the University of Bristol in 2005 and has been a permanent member of academic staff at the University of Glasgow since 2009. His work focuses on the development of machine learning and statistical methods for the analysis of complex data, particularly within the field of computational biology.
\end{IEEEbiography}
\vspace{-1.1cm}
\vskip 0pt plus -1fil
\begin{IEEEbiography}
	[{\includegraphics[width=1in,height=1.25in,clip]{authorpics/dimitris}}]{Dimitrios~P.~Pezaros}
	(S’01–M’04–SM’14) received the B.Sc. and Ph.D. degrees in Computer Science from Lancaster University. He is currently (full) Professor and the founding director of the Networked Systems Research Laboratory at the School of Computing Science, University of Glasgow. He is also a visiting Professor at the University of Athens, Department of Informatics and Telecommunications. Professor Pezaros has published widely in the areas of computer communications, network and service management, and resilience of future networked infrastructures, and has received significant funding for his research from public funding agencies and the industry. He is a Chartered Engineer, and a senior member of the IEEE and the ACM.
